Analysis of pudding following Davidson 1970

### 2025-03-06 inst/pudding.Rmd
tweaks

```{r, makem}
p <- pudding_table
p[1 ,4:6] <- c(10,10,37)  # 1v2
p[2 ,4:6] <- c(10,10,27)  # 1v3
p[4 ,4:6] <- c(10,10,24)  # 1v4
p[7 ,4:6] <- c(10,10,20)  # 1v5
p[11,4:6] <- c(10,10,31)  # 1v6
p
```

@@

```{r,tiepud,cache=TRUE}
Hp <- convert(p)[[2]]
mHp <- maxp(Hp)
mHpt <- mHp[7:12]  #just the tyers
```

@@

```{r,label=savecurlingdataset}
save(pudding_table,pudding,pudding_maxp,curling2_maxp,file="pudding.rda")
```

>>>>

```{r, makem}
p <- pudding_table
p[1 ,4:6] <- c(10,10,37)  # 1v2
p[2 ,4:6] <- c(10,10,27)  # 1v3
p[4 ,4:6] <- c(10,10,34)  # 1v4
p[7 ,4:6] <- c(20,20,10)  # 1v5
p[11,4:6] <- c(10,10,31)  # 1v6
p
```

@@

```{r,tiepud,cache=TRUE}
Hp <- convert(p)[[2]]
options(use_alabama = TRUE)
mHp <- maxp(Hp)
mHpt <- mHp[7:12]  #just the tyers
```

@@

```{r,label=savepuddingdataset}
save(pudding_table, pudding, pudding_maxp, file = "pudding.rda")
```
